\huge Tor's Usability for Censorship Circumvention

### 2016-05-11 pets2017-paper/pets2017-paper.tex
Move autogenerated tables into separate files.

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r r}
	& \multicolumn{2}{r}{success rate} & \multicolumn{1}{r}{median time} &\multicolumn{1}{r}{median}\\
	& \multicolumn{2}{r}{after 40 minutes} & \multicolumn{1}{r}{to success} & \multicolumn{1}{r} {active time} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
	E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
	E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
	E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
	E3-NEW & 13/19 & 68\% & 12:38 & 1:56 \\ 
	E3-OLD & 10/20 & 50\% & 40:08 & 9:06 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

@@

\begin{table}
\centering
% Generated by attempts.R, and manually reordered:
\begin{tabular}{r c c c c c c}
& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
no bridge, no proxy & 17 & 13 &  &  &  &  \\
obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
meek-google, no proxy &  &  &  &  & 5 & 4 \\
meek-azure, no proxy &  &  &  &  & 1 & 1 \\
no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
DNF (did not finish) &  &  &  & 3 & 7 & 9 \\
\end{tabular}
\caption{
Bridge--proxy combinations that led to the first successful bootstrap
in each environment and interface.
Most E1 participants used a direct connection,
but a few tried a built-in obfs3 bridge.
All the E2 participants who succeeded,
did so with obfs3 (the recommended bridge type)---none tried
a different bridge before obfs3.
All of the successful E3 participants but one
used one of the meek bridges.
The remaining E3 participant succeeded in an unexpected way:
by searching the web for an open proxy and configuring it
as the proxy setting.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
	% Generated by info.R:
	\begin{tabular}{l r r r r}
	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
	\noalign{\hrule}
	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
	E2-NEW & 11\% & 83\% & 94\% & 100\% \\
	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
	\end{tabular}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Here, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time. Within 10 minutes, most
participants in E2 had finished, along with a minority of E3 participants. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

>>>>

\begin{table}
\centering
\input{participant-summary.tex}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

@@

\begin{table}
\centering
\input{attempts-bridge-proxy.tex}
\caption{
Bridge--proxy combinations that led to the first successful bootstrap
in each environment and interface.
Most E1 participants used a direct connection,
but a few tried a built-in obfs3 bridge.
All the E2 participants who succeeded,
did so with obfs3 (the recommended bridge type)---none tried
a different bridge before obfs3.
All of the successful E3 participants but one
used one of the meek bridges.
The remaining E3 participant succeeded in an unexpected way:
by searching the web for an open proxy and configuring it
as the proxy setting.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
\input{time_to_success_ecdf.tex}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Here, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time. Within 10 minutes, most
participants in E2 had finished, along with a minority of E3 participants. 
}
\label{fig:time_to_success_ecdf}
\end{figure}
